### 2017-02-24 thesis/results/results2.tex
edited all of the tables and figure captions to something a bit more useful - tmp commit

Pathway associated genetic signatures from the \citet{Gatza2010a} study were examined for their consistency with the reported results.
In the \citet{Gatza2010a} study, their data comprised of samples from different data sets from other studies, \gls{mas}-normalised and the metagene scores were ranked with probit.
However, the analyses so far have used \gls{rma}-normalisation method and ranked based on the number of samples present in the data.
To decide which normalisation or ranking methods were suitable for the analysis, the different methods were compared in Gatza's data (see \cref{app:b}).
Results shown in \cref{app:b} clarified that there was no significant difference in the ranking methods used.
Correlation and scatter plots of the different combinations of transformation matrices (derived from either \gls{rma}- or \gls{mas}-normalised data) with \gls{rma}- or \gls{mas}-normalised data.
It seemed like the normalisation methods of the data in which the transformation matrices were applied to had the most significant effect on the resulting metagenes, rather than the transformation matrices themselves (\cref{app:b}).
This meant that all of the data sets had to be normalised with a single normalisation method, so \gls{rma} normalisation method was used as this method was more reliable than the \gls{mas} method.
Therefore, Gatza's data set was batch corrected first (\cref{sub:batch_correction}), then normalised with \gls{rma} method and the scores were ranked based on the number of samples in the data set.

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=75,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\includegraphics[page=97,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\caption{Example plot}
	\label{fig:gt_rma_vs_mas}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=15,width=0.7\linewidth]{results2/gatza_meta_trans}
	\caption{Gatza metagene direction}
	\label{fig:gatza_meta_dir}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{Spearman correlation of the svd vs tm metagenes (pathway)}
	\label{tab:svd_vs_tm_path}
	\begin{tabular}{lcccc}
		& Gatza & Creighton & Cris & Fuentes-Mattei\\
		\hline
		\hline
		\rule{0pt}{2.25ex}Akt & 1.000 & 0.5190 & 0.5900 & 0.5563 \\
		\gls{bcat}            & 1.000 & 0.9897 & 0.9977 & 0.9905 \\
		E2F1                  & 1.000 & 0.9646 & 0.8438 & 0.9193 \\
		\gls{egfr}            & 1.000 & 0.0430 & 0.3358 & 0.4040 \\
		\gls{er}              & 1.000 & 0.9978 & 0.9942 & 0.9966 \\
		\gls{her2}            & 1.000 & 0.9553 & 0.5817 & 0.9794 \\
		\gls{ifna}            & 1.000 & 0.9830 & 0.9991 & 0.9951 \\
		\gls{ifny}            & 1.000 & 0.9086 & 0.9950 & 0.9718 \\
		Myc                   & 1.000 & 0.9878 & 0.9852 & 0.9689 \\
		p53                   & 1.000 & 0.3808 & 0.9981 & 0.7923 \\
		p63                   & 1.000 & 0.8319 & 0.2951 & 0.8368 \\
		\gls{pi3k}            & 1.000 & 0.9543 & 0.5989 & 0.9365 \\
		\gls{pr}              & 1.000 & 0.9511 & 0.9887 & 0.9845 \\
		Ras                   & 1.000 & 0.9078 & 0.9125 & 0.7229 \\
		Src                   & 1.000 & 0.9575 & 0.7173 & 0.9548 \\
		\gls{stat3}           & 1.000 & 0.1902 & 0.9159 & 0.6167 \\
		\gls{tgfb}            & 1.000 & 0.9918 & 0.2543 & 0.9890 \\
		\gls{tnfa}            & 1.000 & 0.6046 & 0.9365 & 0.4315 \\
		\hline
		\hline
	\end{tabular}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Spearman correlation of the svd vs tm metagenes (obesity)}
	\label{tab:svd_vs_tm_obs}
	\begin{tabular}{lcccc}
		& Creighton & Gatza  & Fuentes-Mattei & Cris\\
		\hline
		\hline
		\rule{0pt}{2.25ex} Cr & 1.000     & 0.9985 & 0.9872 & 0.9161 \\
		Res                   & 1.000     & 0.9987 & 0.9898 & 0.9652 \\
		CrOl                  & 1.000     & 0.9982 & 0.9926 & 0.9715 \\
		ResOl                 & 1.000     & 0.9981 & 0.9927 & 0.9571 \\
		Ca                    & 1.000     & 0.9985 & 0.9893 & 0.9468 \\
		CaRes                 & 1.000     & 0.9988 & 0.9939 & 0.9865 \\
		CaOl                  & 1.000     & 0.9983 & 0.9937 & 0.9677 \\
		CaResOl               & 1.000     & 0.9984 & 0.9952 & 0.9642 \\
		Original              & 1.000     & 0.9928 & 0.9862 & 0.9344 \\
		\hline
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=2,width=0.45\linewidth]{results2/allmetacor_bar}
	\includegraphics[page=16,width=0.45\linewidth]{results2/allmetacor_bar}
	\caption{Visual comparison of the correlation of the metagenes across different data sets}
	\label{fig:allmetacor_bar}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=15,width=0.8\linewidth]{results2/all_meta_trans}
	\caption{All metagenes in Gatza's data}
	\label{fig:gatza_allmeta}
\end{figure}

@@

	\caption{Description of the linear models used to predict the CR obesity metagene}

@@

@@

@@

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
			\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=2,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=3,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=4,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=5,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=6,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=7,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=74,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=71,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=72,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=73,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\caption{Comparison of predicted Cr metagenes with the true Cr metagene in Cris' data}
	\label{fig:predict_cris_cris}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=74,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=71,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=72,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=73,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\caption{Comparison of predicted Cr metagenes with the true Cr metagene in Creighton's data}
	\label{fig:predict_cr_cris}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=8,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=9,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=10,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\caption{Comparison of predicted obesity metagenes with the true obesity metagene in Cris' data}
	\label{fig:stepwise_cris}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=8,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=9,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=10,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\caption{Comparison of predicted obesity metagenes with the true obesity metagene in Creighton's data}
	\label{fig:stepwise_cr}
\end{figure}

>>>>

Pathway associated genetic signatures from the \citet{Gatza2010a} study were examined for their consistency with the reported results.
In the \citet{Gatza2010a} study, their data comprised of samples from different data sets from other studies, \gls{mas}-normalised and the metagene scores were ranked with probit.
However, the analyses so far have used \gls{rma}-normalisation method and ranked based on the number of samples present in the data.
To decide which normalisation or ranking methods were suitable for the analysis, the different methods were compared in Gatza's data (see \cref{app:b}).
Results shown in \cref{app:b} clarified that there was no significant difference in the ranking methods used.
Correlation and scatter plots of the different combinations of transformation matrices (derived from either \gls{rma}- or \gls{mas}-normalised data) with \gls{rma}- or \gls{mas}-normalised data were calculated and plotted.
From these results, it seemed like the normalisation methods of the data in which the transformation matrices were applied to had the most significant effect on the resulting metagenes, rather than the transformation matrices themselves (\cref{app:b}).
This meant that all of the data sets had to be normalised with a single normalisation method, so the \gls{rma} normalisation method was used as this method was more reliable than the \gls{mas} method.
Therefore, Gatza's data set was batch corrected first (\cref{sub:batch_correction}), then normalised with \gls{rma} method and the scores were ranked based on the number of samples in the data set.

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=76,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\includegraphics[page=100,width=0.45\linewidth]{results2/allmeta_rma_vs_mas}
	\caption{Comparison of the metagenes generated in the \gls{mas} normalised Gatza \textit{et al.} data set from the application of the transformation matrices derived from either the \gls{rma} or \gls{mas} normalised data}
	\label{fig:gt_rma_vs_mas}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=15,width=0.7\linewidth]{results2/gatza_meta_trans}
	\caption{Heatmap of all the pathway metagenes from the \citet{Gatza2010a} study in Gatza \textit{et al.} data set}
	\label{fig:gatza_meta_dir}
\end{figure}

@@

\begin{table}[htpb]
	\centering
	\begin{threeparttable}
	\caption{Summary of the Spearman correlations of the pathway metagenes generated from \gls{svd} and the application of the transformation matrices\tnote{1} in Gatza \textit{et al.}, Creighton \textit{et al.}, Print \textit{et al.} and Fuentes-Mattei \textit{et al.} data sets}
	\label{tab:svd_vs_tm_path}
		\begin{tabular}{lcccc}
			& Gatza & Creighton & Cris & Fuentes-Mattei\\
			\hline
			\hline
			\rule{0pt}{2.25ex}Akt & 1.000 & 0.5190 & 0.5900 & 0.5563 \\
			\gls{bcat}            & 1.000 & 0.9897 & 0.9977 & 0.9905 \\
			E2F1                  & 1.000 & 0.9646 & 0.8438 & 0.9193 \\
			\gls{egfr}            & 1.000 & 0.0430 & 0.3358 & 0.4040 \\
			\gls{er}              & 1.000 & 0.9978 & 0.9942 & 0.9966 \\
			\gls{her2}            & 1.000 & 0.9553 & 0.5817 & 0.9794 \\
			\gls{ifna}            & 1.000 & 0.9830 & 0.9991 & 0.9951 \\
			\gls{ifny}            & 1.000 & 0.9086 & 0.9950 & 0.9718 \\
			Myc                   & 1.000 & 0.9878 & 0.9852 & 0.9689 \\
			p53                   & 1.000 & 0.3808 & 0.9981 & 0.7923 \\
			p63                   & 1.000 & 0.8319 & 0.2951 & 0.8368 \\
			\gls{pi3k}            & 1.000 & 0.9543 & 0.5989 & 0.9365 \\
			\gls{pr}              & 1.000 & 0.9511 & 0.9887 & 0.9845 \\
			Ras                   & 1.000 & 0.9078 & 0.9125 & 0.7229 \\
			Src                   & 1.000 & 0.9575 & 0.7173 & 0.9548 \\
			\gls{stat3}           & 1.000 & 0.1902 & 0.9159 & 0.6167 \\
			\gls{tgfb}            & 1.000 & 0.9918 & 0.2543 & 0.9890 \\
			\gls{tnfa}            & 1.000 & 0.6046 & 0.9365 & 0.4315 \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
				\item [1] Transformation matrices were derived from the Gatza \textit{et al.} data set.
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\begin{threeparttable}
		\caption{Summary of the Spearman correlations of the obesity metagenes generated from \gls{svd} and the application of the transformation matrices\tnote{1} in Gatza \textit{et al.}, Creighton \textit{et al.}, Print \textit{et al.} and Fuentes-Mattei \textit{et al.} data sets}
		\label{tab:svd_vs_tm_obs}
		\begin{tabular}{lcccc}
			& Creighton & Gatza  & Fuentes-Mattei & Cris\\
			\hline
			\hline
			\rule{0pt}{2.25ex} Cr & 1.000     & 0.9985 & 0.9872 & 0.9161 \\
			Res                   & 1.000     & 0.9987 & 0.9898 & 0.9652 \\
			CrOl                  & 1.000     & 0.9982 & 0.9926 & 0.9715 \\
			ResOl                 & 1.000     & 0.9981 & 0.9927 & 0.9571 \\
			Ca                    & 1.000     & 0.9985 & 0.9893 & 0.9468 \\
			CaRes                 & 1.000     & 0.9988 & 0.9939 & 0.9865 \\
			CaOl                  & 1.000     & 0.9983 & 0.9937 & 0.9677 \\
			CaResOl               & 1.000     & 0.9984 & 0.9952 & 0.9642 \\
			Original              & 1.000     & 0.9928 & 0.9862 & 0.9344 \\
			\hline
			\hline
		\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
				\item [1] Transformation matrices were derived from the Creighton \textit{et al.} data set.
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=2,width=0.45\linewidth]{results2/allmetacor_bar}
	\includegraphics[page=16,width=0.45\linewidth]{results2/allmetacor_bar}
	\caption{Visual comparison of the Spearman correlations of \gls{svd}-derived and transformation matrix-derived \gls{bcat} and \gls{stat3} metagenes across different data sets}
	\label{fig:allmetacor_bar}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=15,width=0.8\linewidth]{results2/all_meta_trans}
	\caption{Heatmap of all the pathway and obesity metagenes in Gatza \textit{et al.} data set}
	\label{fig:gatza_allmeta}
\end{figure}

@@

	\caption{Description of the linear models used to predict the CR obesity metagene in Print \textit{et al.} data set}

@@

			\begin{footnotesize}

@@

			\end{footnotesize}

@@

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene in Print \textit{et al.} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=2,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=3,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=4,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=5,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=6,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=7,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=74,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=71,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=72,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\includegraphics[page=73,width=0.32\linewidth]{results2/prediction_cris_with_cris(cris_model)}
	\caption{Comparison of the predicted Cr metagenes with the true Cr metagene in the Print \textit{et al.} data}
	\label{fig:predict_cris_cris}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=74,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=71,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=72,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\includegraphics[page=73,width=0.32\linewidth]{results2/prediction_cr_with_cris}
	\caption{Comparison of the predicted Cr metagenes with the true Cr metagene in the Creighton \textit{et al.} data}
	\label{fig:predict_cr_cris}
\end{figure}

@@

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=8,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=9,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\includegraphics[page=10,width=0.32\linewidth]{results2/stepwise_cris_cris}
	\caption{Comparison of the predicted obesity metagenes with the true obesity metagene in Print \textit{et al.} data}
	\label{fig:stepwise_cris}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[page=1,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=2,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=3,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=4,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=5,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=6,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=7,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=8,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=9,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\includegraphics[page=10,width=0.32\linewidth]{results2/stepwise_cr_cris}
	\caption{Comparison of the predicted obesity metagenes with the true obesity metagene in Creighton \textit{et al.} data}
	\label{fig:stepwise_cr}
\end{figure}
